### 2020-06-01 report/sections/server/codegen/workflow.tex
Report: progress on chapter 3

% input: protocol, role, target
% then: verify well-formedness
% then: obtain EFSM for role
% then: parse EFSM
% then: generate code for said target
% output: API

We motivate our development workflow from previous work 
\cite{PureScript2019} by extending the \fancyname{Scribble} toolchain
and generating APIs that integrate developer implementation
into the EFSM execution.

@@

\begin{itemize}
\item see notes from PLACES paper on scribble
\item scribble language definition (unless already in background)
\end{itemize}

>>>>

We motivate our development workflow from previous work 
\cite{PureScript2019} by extending the \fancyname{Scribble} toolchain
and generating APIs that integrate the developer's 
application logic
into the execution of the communication automata.

@@

We use the \fancyname{Scribble} protocol description language, 
as presented in
\cite{Scribble}, for formalising the communication structure. This is
inspired by existing work on implementing session type theory 
in mainstream programming languages
\cite{Hybrid2016, PureScript2019, Python2017}. 
We use the variant of the \fancyname{Scribble} language 
previously introduced in \cref{subsection:bgscribble}.

\subparagraph{Type declaration statements}
Specific to our TypeScript API generation toolchain,
the developer is \textit{not} required to explicitly
add type declaration statements for built-in types.
\cref{lst:adder} is a \textit{syntactically correct}
\fancyname{Scribble} protocol as far as 
\fancyname{SessionTS} is concerned. 
Internally, \fancyname{SessionTS} inspects the protocol file
and parses existing type declarations using regular expressions
(or \textit{regex}) -- this is necessary to extract any
custom data types that will appear in the communication (for example,
\cref{lst:game}), and allows \fancyname{SessionTS} to inject
``boilerplate'' type declarations for built-in TypeScript types before
calling \fancyname{Scribble}.

\begin{figure}[!ht]
\begin{lstlisting}[language=Scribble]
module Adder;

global protocol Adder(role Client, role Svr) {
	choice at Client {
		ADD(number, number) from Client to Svr;
		RES(number)         from Svr to Client;	
	} or {
		QUIT(string) from Client to Svr;	
		TERMINATE()  from Svr to Client;
	}
}
\end{lstlisting}
\captionof{lstlisting}{The \tprotocol{Adder} Protocol}
\label{lst:adder}
\end{figure}

We will use the \tprotocol{Adder} protocol as a running example
to demonstrate how our work performs TypeScript API generation.
